Music Adaptation: Analysis for selected stimuli

### 2021-02-16 material/expstimuli/tweaked/analysis.Rmd
add hline
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>
calculate new time (timeFixed for offsets) based on fixedKOT
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

- There are 4 base tempi

@@

## Mean
```{r ioi-mean, echo = FALSE}
# mean
dt_ioi[SubArt != "NA", .(N = .N, Mean = mean(IOI), SD = sd(IOI)), "MidFile"]

ggboxplot(dt_ioi[SubArt != "NA"], x = "MidFileShort", y = "IOI", add = "jitter", width = 0.8)
```

# KOT

@@

## Tweak
```{r kot-tweak, echo = FALSE}
# grandMean of art_only & high stimuli
kot_grandMean <- mean(dt_kot[grepl("art_only", MidFile) | grepl("high", MidFile) & SubArt != "NA"]$KOT)

@@

>>>>

- There are 4 base tempi.

@@

## Mean
- The red line indicates the ideal tempo (100bpm - IOI: 300 ms)

```{r ioi-mean, echo = FALSE}
# mean
dt_ioi[SubArt != "NA", .(N = .N, Mean = mean(IOI), SD = sd(IOI)), "MidFile"]

ggboxplot(dt_ioi[SubArt != "NA"], x = "MidFileShort", y = "IOI", add = "jitter", width = 0.8) + geom_hline(yintercept = 300, linetype = "dashed", color = "red")
```

# KOT
- For art_only and high stimuli, there should be a bimodal distribution to represent legato and staccato.

- For dyn_only and low stimuli, there should be a normal distribution.

@@

## Tweak
- For dyn_only and low stimuli, it seems the KOT values are too close to the staccato range. We calculated the difference between the mean of each stimulus and the grand mean of art_only and high stimuli and add that difference to all KOT values for dyn_only and low, so that the KOT values should shift closer to the grand mean of art_only and high stimuli.

```{r kot-tweak, echo = FALSE}
# grandMean of art_only & high stimuli
kot_grandMean <- mean(dt_kot[grepl("art_only", MidFile) | grepl("high", MidFile) & SubArt != "NA"]$KOT)

@@

# Export stimuli with fixed KOT as mid files
```{r export, include = FALSE}
# fix time for onset and offset data
data_offset$timeFixed <- data_onset$time
data_offset$timeFixed <- data_offset$time
for (midfile in unique(tweak_data$MidFile)){
   # offset[i] = onset[i+1]+KOT[i]
   for (i in 1:nrow(data_onset[MidFile == midfile])-1){
      data_offset[MidFile == midfile][i]$timeFixed <- data_onset[MidFile == midfile][i+1]$time+dt_kot[MidFile == midfile][i]$FixedKOT
   }
}

for (stim in unique(data_onset$MidFile)){
   onset <- data_onset[MidFile == stim]
   offset <- data_offset[MidFile == stim]
   instance <- rbind(onset, offset)
   # round timeFixed
   instance$timeFixed <- round(instance$timeFixed, 0)
   # Note_On/Off >> 1 or 0
   instance$KeyOnOff <- 0
   instance[event == "Note On"]$KeyOnOff <- 1
   # sort by timeFixed
   instance <- instance[order(timeFixed)]

   filename = paste(stim, ".txt", sep = "")
   fwrite(instance, filename)
}
```

```{bash, echo = TRUE}
# python
source /Users/atsukotominaga/Pyenv/bin/activate
python mid_export.py
```
